### 2016-01-26 hans/bayes-tardis-luminosity-prediction.tex
[draft] separate #packets for paramater and Poisson inference

>>>>

\fred{We should be more general: let's reserve $n$ for the number of
  packets observed in a bin. Suppose this is $n=1$. From that, we can
  hardly infer the luminosity distribution. Instead, we group the
  packets in larger bins such that there are at least $m \gtrsim 300$
  packets, and then assume the distribution doesn't change much with
  frequency.

  Hence we will learn $\bmphi$ from $m$ samples, and
  $p(\bmphi\cond N,n,\bml) \to p(\bmphi\cond N,m,\bml)$ and we can
  keep $\bml$ with the same meaning. So we replace $n \to m$ below
  except in $p(N \cond n$)}
